Adapting the MVDR to a GPU for active sonar systems of different sizes.

### 2013-01-22 ASA2013/asa2013.tex
la2pdf commit - 2013:01:22	16:21:12	(Tue22.Jan)

Graphics Processing Units (GPUs) is a technology tailored to perform image processing at incredible speeds. They are available off-the-shelf at reasonable prices, are very power efficient, and can be programmed to carry out a wide range of computational tasks, often displaying an order of magnitude speedups compared to comparable designs running on a CPU. Initially, GPU may seem perfectly suited for image reconstruction algorithms, because usually each pixel can be computed independently and concurrently of one another. While this is true for simple techniques such as conventional beamformers, the more complex per-pixel computations present in adaptive techniques are harder for the GPU to handle.

>>>>

Graphics Processing Units (GPUs) is a technology tailored to perform image processing at incredible speeds. They are available off-the-shelf at reasonable prices, are very power efficient, and can be programmed to carry out a wide range of computational tasks, often displaying an order of magnitude speedups compared to similar CPU designs. Initially, GPUs may seem perfectly suited for image reconstruction algorithms, because usually each pixel can be computed independently and concurrently of one another. While this is true for simple techniques such as conventional beamformers, the more complex per-pixel computations present in adaptive techniques are harder for the GPU to handle.
